A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-06-29 manuscript/CI_interactions.tex
added t-tests from simulation to supplemental. Just waiting for Tomas comments, then ready to submit

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Article type: Ideas and Perspectives
% \item Number of references: 36
% \item Number of figs, tables, \& text boxes: 8 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Text box 1 word count: 381
% \item Text box 2 word count: 210
% \item Abstract word count: 199
% \item Main text word count: 7078 % Including 31 page numbers. Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

% \linenumbers
\clearpage

@@

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths. To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. 
    % Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web and, finally, illustrate this framework using an extensively sampled empirical network.
    % We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

@@

        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$). An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}). 
        % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions? 
        This is not possible, however, using empirical data. An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        % The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur? How may we refine our sampling approaches to reduce uncertainties and gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits). Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?

@@

  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript and K\'{e}vin Cazalles for providing feedback. The authors appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR) from Formas for grant \#942-2015-1262 (to AE).

@@

\captionsetup{singlelinecheck=false, font={stretch=1}}

@@

% \begin{fullbox}{}
%   \begin{spacing}{1.0}
%     \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
%     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
%     \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}C).
%   \end{spacing}
% \end{fullbox}

% \clearpage

  \begin{figure}[h!]
    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site. Interaction uncertainty means that some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
    Process uncertainty describes the fact that interactions occur with different probabilities during any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
    After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction depending on the interaction, process, and detection uncertainty associated with it. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.}
    \label{conceptual_fig}
    \begin{center}
    \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that did co-occur rarely interacted. \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution. Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high. }
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$). 
    Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    \end{center}
    \end{figure}

  % \begin{figure}[h!]
  %   \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. \textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda_{ij}$ when $n$=0 was (0.013, 0.049). We can therefore be at least 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence of species $i$ and $j$. To be confident that $\lambda_{ij}$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset. \textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda_{ij}$ was substantially broader and many observed co-occurrences ($\approx$ 15-35) are required to be 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05.}
  %   \label{Salix_cdfs}
  %   \begin{center}
  %   \includegraphics[width=.5\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
  %   \end{center}

  %   \end{figure}

  \begin{figure}[h!]
    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range. To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks. The detection-filter networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases. Values in the original web are indicated by dashed lines.}
    \label{posterior_webs}    
    \begin{center}
    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
    \end{center}
    \end{figure}

>>>>

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 6 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6872 % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

\linenumbers
\clearpage

@@

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths. To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.

@@

        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$). An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}). 
        This is not possible, however, using empirical data. An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

@@

  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript and K\'{e}vin Cazalles for providing feedback. The authors appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR) and from Formas for grant \#942-2015-1262 (to AE).

@@

\captionsetup{singlelinecheck=false, font={stretch=2}}

@@

  \begin{figure}[h!]
    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site. Interaction uncertainty means that some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
    Process uncertainty describes the fact that interactions occur with different probabilities during any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
    After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction depending on the interaction, process, and detection uncertainty associated with it. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that did co-occur rarely interacted. \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution. Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high. }
    \label{upper_limits}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$). 
    Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range. To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks. The detection-filter networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases. Values in the original web are indicated by dashed lines.}
    \label{posterior_webs}    
    \begin{center}
    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
    \end{center}
    \end{figure}

### 2018-06-29 manuscript/coverletter.tex
added t-tests from simulation to supplemental. Just waiting for Tomas comments, then ready to submit

    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. The goals of this manuscript are A) to illustrate the extreme difficulty in fully sampling the set of interactions occurring within a community, B) to demonstrate the construction of networks treating each interaction probabilistically (based on prior information as well as available data), and C) to offer concrete recommendations that will facilitate the use of this framework in future work.

    We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community. Some interactions may be rare because of species traits (e.g., prey that are only consumed by the largest individuals of a predator species), others may be difficult to detect because they occur under conditions not conducive to sampling (e.g., during inclement weather or at night), and yet other interactions may be common but very difficult to detect (e.g., interactions involving species that are highly cryptic). We emphasise that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix. We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017. \textbf{Ecology} 98: 1730).

    With extensive sampling being time- and resource-intensive and not a complete solution to the problems posed by interaction uncertainty, we suggest that researchers instead treat interactions probabilistically and incorporate prior information to set bounds on the probability of interaction between species that were not observed interacting. As mentioned above, a lack of observed interaction could have several causes and does not necessarily imply that the interaction truly does not occur. We demonstrate a simple Bayesian framework, including the selection of a prior distribution, and use it to predict the likely set of feasible interactions in our example \emph{Salix} system. Based on this framework, we close with a set of recommendations for both empiricists and theoreticians that should improve our ability to deal with the uncertainty inherent in ecological networks and compare networks across systems.

    We are aware that there are several studies already using various forms of Bayesian networks to treat interactions as probabilities. These efforts have, however, so far remained confined to fairly theoretical work. We believe that empirical ecologists will also find Bayesian networks a useful tool when planning field sampling and when describing and analysing their focal communities. Our goal with this manuscript is, therefore, to introduce a Bayesian line of thought in as approachable and broadly-applicable terms as possible. To that end, we provide simple R code that illustrates each step of our approach.

@@

% Pedro Jordano pedroj@me.com Estacion Biologica de Donana CSIC
% Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC) 
% Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg
% Paolo Guimaraes
% Jason Tylianakis
% ask Tomas for empiricists
% Owen Petchey

>>>>

    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. The goals of this manuscript are to demonstrate the extreme difficulty of observing all interactions that occur within a community and, given this difficulty, to illustrate a framework for combining prior knowledge about the system with observed data in order to gauge the probability of interactions which were not observed. We close by offering concrete recommendations that will facilitate researchers' efforts to acknowledge and set bounds on the uncertainty inherent in ecological data.

    We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community. Interactions may not be observed because a species is rare and does not encounter its partner during sampling, because environmental constraints prohibit the interaction during sampling, because one or both species is difficult to observe in the field, or because the interaction truly does not occur. We emphasise that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix. We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017. \textbf{Ecology} 98: 1730).

    In many cases, it will not be feasible to sample all species pairs intensively enough (tens of observations per pair) to be confident that the pair does not interact. Given the time and resource constraints that often restrict fieldwork, we suggest that researchers supplement observed data with prior information about the system. Thus, they can set bounds on the probability of interaction between species that were not observed interacting. We demonstrate this simple Bayesian framework, including the selection of a prior distribution, and use it to predict the likely set of feasible interactions in our example \emph{Salix} system. Based on this framework, we close with a set of recommendations for both empiricists and theoreticians that should improve our ability to deal with the uncertainty inherent in ecological networks and compare networks across systems.

    We are aware that there are several studies already using various forms of Bayesian networks to treat interactions as probabilities. These efforts are, however, generally confined to fairly theoretical work. We believe that empirical ecologists will find Bayesian interaction probabilities to be a useful tool when planning field sampling and when describing and analysing their focal communities. Our goal with this manuscript is, therefore, to introduce a Bayesian line of thought in as approachable and broadly-applicable terms as possible. To that end, we provide simple R code that illustrates each step of our approach.

@@

% Pedro Jordano pedroj@me.com Estacion Biologica de Donana CSIC
% Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC) 
% Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg
% Paolo Guimaraes 
% Jason Tylianakis jason.tylianakis@canterbury.ac.nz :)
% ask Tomas for empiricists
% Owen Petchey University of Zurich owen.petchey@ieu.uzh.ch
